\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.00in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=-0.05in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Soham Jain} \\ \vspace{6pt}
    \small 240-728-8946 $|$ \href{jainsoham01@gmail.com}
    {\underline{jainsoham01@gmail.com}} $|$ 
    \href{https://sjain2025.github.io/}
    {\underline{sjain2025.github.io}} $|$ 
    \href{https://www.linkedin.com/in/soham-jain1/}
    {\underline{linkedin.com/in/soham-jain1}} $|$
    \href{https://github.com/sjain2025}{\underline{github.com/sjain2025}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{May 2028}
      {B.S. in Computer Science, Concentration in Machine Learning}{Pittsburgh, PA}
      \resumeItemListStart
            \resumeItem{\textbf{Relevant Courses:} Data Structures \& Algorithms, Computer Systems, Functional Programming, Discrete Math, Linear Algebra, Artificial Intelligence, Machine Learning, Computer Vision, Mobile \& Web App Development}
  \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.00in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, C++, JavaScript, TypeScript, C\#, SQL, HTML, CSS} \\
     \textbf{Developer Tools}{: Git, Linux/Unix, Docker, Railway, AWS, Google Cloud Platform, Firebase, MongoDB} \\
     \textbf{Frameworks \& Libraries}{: React, Vite, Node.js, Flask, Express, Next.js, OpenCV, NumPy, Pandas, TensorFlow, Keras} \\
    }}
 \end{itemize}
 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Aug 2025 -- Present}
      {ScottyLabs}{Pittsburgh, PA}
      \resumeItemListStart
        \resumeItem{Integrating live data from Dining Services into CMUEats using React, TypeScript, and Railway, streamlining menus and specials for 10,000+ users each month across mobile and web.}
        \resumeItem{Leading the development of a geospatial routing system with JavaScript and REST APIs to rank dining locations by walking distance, resulting in a 30-50\% reduction in time to find dining locations.}
        \resumeItem{Designing CI/CD workflows for 50+ developers with GitHub Actions and Docker to enforce linting and unit testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{May 2022 -- Feb 2025}
      {Vytal.AI}{Alexandria, VA}
      \resumeItemListStart
        \resumeItem{Developed a mobile application that analyzes ocular biometrics using OpenCV, Next.js, and MongoDB to quantify brain health in under 30 seconds.}
        \resumeItem{Optimized Python pipelines and deployed ML models on AWS EC2 to scale testing to 300+ clinical beta users.}
        \resumeItem{Implemented OCR-driven PDF parsing using Agile methodologies like sprint cycles and stand-ups, decreasing the average processing time for uploaded health records by 90 seconds.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Science Research Intern}{Apr 2024 -- Jan 2025}
      {Virginia Tech}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Constructed algorithms for constraint satisfaction problems in C\# and Python to reduce computation time by up to 65\% compared to leading recursive methods.}
        \resumeItem{Applied object-oriented architecture for graph nodes and edges to compute a valid four-coloring of the U.S. map.}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Research Intern}{Jun 2023 -- Jan 2024}
      {George Mason University}{Fairfax, VA}
      \resumeItemListStart
        \resumeItem{Built a web dashboard using Flask, HTML/CSS, and Matplotlib to standardized metrics for analyzing the technical performance of molecular dynamics simulations.}
        \resumeItem{Published first-author paper in the Journal of Student-Scientists’ Research, amplifying real-world impact.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
% -------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RoutineRemind}}{Jun 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a patent-pending iOS/Android app with JavaScript, HTML, and Firebase that uses audio classification and natural language processing to help children with autism personalize daily schedules.}
            \resumeItem{Implementing secure user authentication with Firebase to manage over 200 active student and caregiver accounts.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{EyeLS}}{Aug 2023 -- Sep 2025}
          \resumeItemListStart
            \resumeItem{Constructed an eye-tracking application with OpenCV and TensorFlow to map eye movements to click locations with 92\% calibration accuracy, enabling patients with ALS to communicate non-verbally.}
            \resumeItem{Granted the IEEE Technical Excellence Award for innovating a cost-effective alternative to \$15,000+ AAC devices.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{LapseNet}}{Mar 2024 -- Dec 2024}
          \resumeItemListStart
            \resumeItem{Deployed a Python and SQL video data pipeline to train a deep learning system for real-time fall detection, achieving a 99\%+ classification accuracy in training and testing.}
            \resumeItem{Recognized with the Best Presentation Award at the 6th International Conference on Robotics and Computer Vision.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%

%-------------------------------------------
\end{document}